### 2023-02-06 manuscript.tex
Merge pull request #305 from fhillemann/fhillemann-fig-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/62e51b8b993037bb5cc302309cb8c9b983e00378.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/62e51b8b993037bb5cc302309cb8c9b983e00378/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4108433864

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/659dbf07d94474726c8403d04555afbb3a45da57/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/659dbf07d94474726c8403d04555afbb3a45da57}{SORTEE-Github-Hackathon/manuscript@659dbf0}
on February 6, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/62e51b8b993037bb5cc302309cb8c9b983e00378/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/62e51b8b993037bb5cc302309cb8c9b983e00378}{SORTEE-Github-Hackathon/manuscript@62e51b8}
on February 6, 2023.
